Teaching Low-Level Concurrency with \pebbles and \landslide

### 2016-08-27 sigcse-17/410.tex
sigcse: some more help from garth

The first project is a backtrace library: %``stack crawler'':
when invoked by a client program, it displays the
%program's
stack symbolically,
showing function names, strings, floating-point values, etc.
This project
%\shortversion{enables}{meets a variety of goals: it enables}
%students to review key process-model and
%language-runtime concepts from the
%prerequisite course;
%it
introduces students to course expectations about
design, analysis, and making choices;
%finally,
and
because C pointers are unsafe, it requires students
to consider robustness.
%
% and we READ THEIR CODE
% ^^ LOL, classic dave.
This project is built using a standard C tool chain
% FIXME garth wants to cite gdb
and debugged as students see fit (generally \x{printf()} and GDB).

@@

\textbf{Time.}
Being a high-level systems elective, \fourten is exceptionally time-consuming,
demanding 20 or more hours weekly during the hardest projects. %thread library and kernel projects.
A more accessible version of the course could be implemented
by extending the time available for the first three projects
and concluding with a stripped-down subset of the kernel,
or by offering the kernel project in an optional second semester.

>>>>

The first project is a backtrace library: %``stack crawler'':
when invoked by a client program, it displays the
%program's
stack symbolically,
showing function names, strings, floating-point values, etc.
This project
%\shortversion{enables}{meets a variety of goals: it enables}
%students to review key process-model and
%language-runtime concepts from the
%prerequisite course;
%it
introduces course expectations about
design, analysis, and making choices;
%finally,
and
because C pointers are unsafe, it requires students
to consider robustness.
%
% and we READ THEIR CODE
% ^^ LOL, classic dave.
This project uses a standard C tool chain
% FIXME garth wants to cite gdb
and debugged as students see fit (generally GDB, a symbolic debugger, and \x{printf}).

@@

\textbf{Time.}
%% garth's version
Being a high-level systems elective, \fourten is exceptionally time-consuming,
especially during the thread library and kernel projects.
It could be revised to fit another program's available time and effort
levels by extending the time available for the first three projects,
ending with the thread library, and optionally offering the kernel
project in a specialized second semester course.

%% my version
%Being a high-level systems elective, \fourten is exceptionally time-consuming for students,
%especially during the thread library and kernel projects.
%A more accessible version of the course could be implemented
%by extending the time available for the first three projects
%and concluding with a stripped-down subset of the kernel,
%or by offering the kernel project in an optional second semester.
